% Created 2017-05-15 Mon 10:46
% Intended LaTeX compiler: pdflatex
\documentclass[presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[version=3]{mhchem}
\usepackage[numbers,super,sort&compress]{natbib}
\usepackage{natmove}
\usepackage{url}
\usepackage{minted}
\usepackage{underscore}
\usepackage[linktocpage,pdfstartview=FitH,colorlinks,
linkcolor=blue,anchorcolor=blue,
citecolor=blue,filecolor=blue,menucolor=blue,urlcolor=blue]{hyperref}
\usepackage{attachfile}
\usetheme{default}
\author{Reyer and Jan}
\date{\today}
\title{Agenda}
\begin{document}

\begin{frame}{Outline}
\tableofcontents
\end{frame}





\begin{frame}[label={sec:org3af1b58}]{announcements}
\begin{itemize}
\item 100\% BKO
\item planned date to move to P: 19 and 20 July
\item we've started the appraisal interviews
\begin{itemize}
\item if you have feedback for us feel free to give this
\item we will also create a webform to give feedback
\end{itemize}
\item things we are thinking about at the moment:
\begin{itemize}
\item criteria for sponsored chairs
\item next year's thesis allocation
\item talk to us if you have ideas about these
\end{itemize}
\end{itemize}
\end{frame}



\begin{frame}[label={sec:orgbabc164}]{tenure and promotion procedure}
\begin{itemize}
\item we have the new procedure now for over a year
\item we promised to review it after a year
\item we want to collect your ideas
\item if you want to change things, you can make proposals and we vote on them
\end{itemize}


\begin{block}{positive feedback we received}
\begin{itemize}
\item we have clear procedure now
\item it is democratic
\item AIS scores seem more reasonable than narrowly defined Center-journal-lists
\begin{itemize}
\item do we use the right benchmark values? Should they be higher/lower?
\end{itemize}
\end{itemize}
\end{block}



\begin{block}{concerns}
\begin{itemize}
\item the speed of the procedure
\begin{itemize}
\item both a dept. procedure and one at TiSEM
\end{itemize}
\item effort investment by committee
\begin{itemize}
\item one suggestion: perhaps there are cases where the committee does not need to read papers
\end{itemize}
\item (mis)match between dept. and faculty procedure
\begin{itemize}
\item both in terms of criteria and procedure
\end{itemize}
\item how should we deal with external money being brought in?
\begin{itemize}
\item count as AIS points? Good citizenship?
\end{itemize}
\item the way we evaluate education: we have not yet received proposals on this.
\end{itemize}
\end{block}


\begin{block}{criteria academic directors}
\begin{itemize}
\item people who do not satisfy the standard tenure/promotion criteria
\begin{itemize}
\item e.g. anyone with a major admin task
\item like academic directors
\end{itemize}
\item we have tried to create ex ante criteria
\begin{itemize}
\item like every year of AD counts as \(x\) AIS points
\item but we didn't manage
\end{itemize}
\item our suggestions is to have a personal plan for people that do not satisfy the standard tenure/promotion criteria
\item but then we need to be able to commit to AD's about tenure and promotion
\item we will have a dept. meeting in which we explain our decision and you can ask questions but there will not be a vote
\end{itemize}
\end{block}
\end{frame}
\end{document}